---
title: "Physiology of `r params$pick_species` Penguins "
author: "Minnie"
output: html_document
params:
  pick_species: Gentoo
---

### Your job: create a parameterized report using data from `penguins.csv`. 
- Your report should contain a ggplot graph of flipper length versus body mass for the **species** that you choose.

- In the `render_functions.R` script, create a function that will render the report for the species you pick, saved as an .html with format 'penguin_report_SPECIESNAME.html'. 

- In the `render_functions.R` script, write a for loop that will automatically render a separate report for *all species* in the data. 



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

penguins <- read_csv("penguins.csv")

```
You have chosen to examine penguin species: `r params$pick_species`


```{r}
penguin_subset <- penguins %>% 
  filter(species == params$pick_species)

ggplot(data=penguin_subset) +
  geom_point(aes(x=flipper_length_mm, y=body_mass_g, color = island, size = species)) +
  labs(x = "Flipper Length(mm)", y = "Body Mass (g)", color = "Island")
```


